Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-07-27 apj.tex
edit text

Our model $\gamma$-based vectors can be written in terms of the 
dust-based $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $\mathbf{a}$ and $\mathbf{b}$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V} \\
\frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
2.82 & 1.15  \\
-5.27 & 0.72
\end{array}
\end{pmatrix} 
\begin{pmatrix}
\mathbf{a} \\
\mathbf{b}
\end{pmatrix}+
\begin{pmatrix}
\pmb{\epsilon}_{\gamma^0} \\
\pmb{\epsilon}_{\gamma^1}
\end{pmatrix},
\label{trans_I:eqn}
\end{equation}
where the two residual vectors
\begin{align}
\begin{split}
\pmb{\epsilon}_{\gamma^0} &=(0.06, -0.07, -0.07,  0.07, 0.02), \\
\pmb{\epsilon}_{\gamma^1} & =(-0.06, 0.16, -0.22, 0.33, -0.26)
\end{split}
\label{res_I:eqn}
\end{align}
quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.
This result indicates that
the allowed variations in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to near-parallel 2-dimensional
planes within
the 5-dimensional magnitude space.
Wiith no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.

@@

%The dust model expressed in Eqn.~\ref{f99:eqn} can be reparameterized as
%\begin{equation}
%A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
%\label{f99:eqn}
%\end{equation}
%where $R=A_V/E(B-V)$.

Suppose that the data were due to a dust model with constant $R \equiv A_V/E(B-V)$.
The  $A_V$ and $E(B-V)$ parameters of the dust model in Eqn.~\ref{f99:eqn} would then be correlated.
An alternative parameterization 
\begin{equation}
A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
\end{equation}

A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models.
These determine the choice of directions of
the vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
and so the $\gamma$'s

   Then a \citetalias{1999PASP..111...63F}  dust model 
can be written in a new basis
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the parameters $\kappa_1$ and $\kappa_2$ parameterizing the directions of the two new basis vectors.
The vector $a(X)+\kappa_1 b(X)$ represents extinction that can occur with fixed $R^F_0=1/\kappa_1$ and unconstrained $\kappa_2$.
%While a similar interpretation could be made of $\kappa_2 a(X) + b(X)$, note that to first order the extinction for $\Delta R$
%perturbations from a fixed $R^F_0$ is
%\begin{equation}
%A_X = A_V \left(a(X) + \left(\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0} \right) b(X) \right).
%\end{equation}
%Then $\kappa^{-1}_2$ can this be associated with $\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0}$.

\color{purple}
The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$, $\kappa_2=-5.27/0.72=-7.31$.
The directions of the $\pmb{\gamma}$ vectors, and  the expectations from  \citetalias{1999PASP..111...63F} with $R=\kappa^{-1}$, are shown in 
Figure~\ref{plane:fig}.  There is almost perfect alignment between $\pmb{\gamma}^0$ and $R=2.44$ dust.
 From the Monte Carlo chains, we find a 68\% credible interval for $\kappa^{-1}_1$ of 2.26--2.63.

To gain an intuitive understanding of how the $\kappa$ values are determined, consider the hypothetical case where
all supernovae experience dust with the same $R^F$.   There is only one free parameter $A^F_V$ and magnitudes are
constrained to move along the vector $a(X)+b(X)/R^F$.  In the fit of the linear model, the zero-covariance condition is satisfied when
$-\kappa_1 A^F_V + E^F(B-V)=0$,  i.e.\ when $\kappa_1=1/R^F$.  
Supernova magnitudes do not vary along the $\kappa_2 a(X) + b(X)$ direction.  Consequently
$\pmb{\gamma}^0$ is aligned with  $a(X)+b(X)/R^F$, and $\pmb{\gamma}^1$ is unconstrained.

Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
The zero-correlation condition, which determines the direction of $\pmb{\gamma}^1$,  is for the coordinate values along $\pmb{\gamma}^0$ to be uncorrelated with the coordinate values along $\pmb{\gamma}^1$.
Our analysis yields an angle of 154\arcdeg\ between  $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\pmb{\gamma}^0$.

\color{purple}
As a check of our analysis implementation, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample
(making an approximative correspondence between our observed top-hat filter colors and the 
model parameter $E^F(B-V)$) , and $R^F$ values drawn from a log-normal
distribution with a mean of $\ln{2.5}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations: the input $R^F=2.5$ is centered
within the 68\% credible interval for $\kappa^{-1}_1$ of 2.38--2.69.

@@

Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
the former's distribution can be compared to the expectation for the latter.
Figure~\ref{k0_med:fig} shows the histogram of
median values of $\gamma^0_V k_0$ 
\color{purple}
relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
()
\color{black}
The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.  This distribution is given by the data, in that it is independent of any knowledge or prior
for the distribution of dust extinction the SN population is expected to suffer.

Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which can be attributed to 
extinction corrections due to deviations away from the canonical $\kappa_1$ value.   The distribution has a long
negative tail and is peaked at its positive edge, and by construction has a mean of zero.
The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
of negative values associated with $R<1/\kappa_1$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$
%\color{purple}
%While at low  $\gamma^0_V k_0$
%\color{black}
%On the other hand, lower values of $\gamma^1_V k_1$
%occur at larger values of  $\gamma^0_V k_0$.
These findings are consistent with previous results:
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
%\citet{2011ApJ...729...55F} and the above authors
%find that supernovae with large extinction 
%preferentially exhibit low $R^F$.

@@

In the fit to our model, the observed color excess is attributed to 
%----
$E_{\gamma^0}(B-V)=  0.90 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.34 \pm   0.10$
%-----
contributions.
Among the supernovae in the SNfactory  set used to determine $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$, the
objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
%---
$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have$-0.01 \pm 0.01$  and
$  0.06 \pm 0.03$ 
%---
(see Figure~\ref{ebv:fig}).
The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
span of supernovae used to train the coefficients of the model, which is not unexpected if
attributable to dust.

\color{purple}
Our model can be associated with the extinction model of  \citetalias{1999PASP..111...63F} using Eqn.\ref{trans_I:eqn}
and the assumption that  SN~2011fe has zero extinction.  Transforming our parameters to those
of   \citetalias{1999PASP..111...63F}, we obtain
$A^F_V=0.77$ and $E^F(B-V)=1.28$ with covariance
\begin{equation}
\begin{pmatrix}
\begin{array}{rr}
0.430 & -0.004 \\
-0.004 & 0.007
\end{array}
\end{pmatrix},
\end{equation}
which implies $R^F= 0.59^{+ 0.53}_{-0.48}$.
The color excesses predicted by these values are shown in Figure~\ref{sn2014j:fig}.

The imperfect correspondence between our model and that of   \citetalias{1999PASP..111...63F} is seen in Figure~\ref{sn2014j:fig}.
While both models reproduce the observed color excesses at the extreme $U$ and $I$ bands,  \citetalias{1999PASP..111...63F}'s
does not simultaneously match the central colors.
The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
in Figure 3 of  \citet{2014ApJ...788L..21A}.  (They use
UV through NIR data to fit \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$.)
Our model predictions provide a significantly better match to the data
despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.

>>>>

Our model $\gamma$-based vectors can be written in terms of the 
dust-based $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $\mathbf{a}$ and $\mathbf{b}$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V} \\
\frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
2.82 & 1.15  \\
-5.27 & 0.72
\end{array}
\end{pmatrix} 
\begin{pmatrix}
\mathbf{a} \\
\mathbf{b}
\end{pmatrix}+
\begin{pmatrix}
\pmb{\epsilon}_{\gamma^0} \\
\pmb{\epsilon}_{\gamma^1}
\end{pmatrix},
\label{trans_I:eqn}
\end{equation}
where the two residual vectors
\begin{align}
\begin{split}
\pmb{\epsilon}_{\gamma^0} &=(0.06, -0.07, -0.07,  0.07, 0.02), \\
\pmb{\epsilon}_{\gamma^1} & =(-0.06, 0.16, -0.22, 0.33, -0.26)
\end{split}
\label{res_I:eqn}
\end{align}
quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.  The most significant
deviation away from the plane is in the $R$-band.
This result indicates that
the allowed variations in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to near-parallel 2-dimensional
planes within
the 5-dimensional magnitude space.
Wiith no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.

@@

%The dust model expressed in Eqn.~\ref{f99:eqn} can be reparameterized as
%\begin{equation}
%A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
%\label{f99:eqn}
%\end{equation}
%where $R=A_V/E(B-V)$.
\color{purple}
In principle, our linear model could accommodate for $\gamma$ any two independent vectors that span
the plane.  We begin discussion on the specific choice of $\gamma$ returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model. 
While
Eqn.~\ref{f99:eqn} expresses that model using basis vectors $\mathbf{a}$ and $\mathbf{b}$ and
their corresponding parameters 
$A_V$ and 
$E(B-V)$, the linear dust model could be written in terms of any two other basis vectors  $\mathbf{a}+\kappa_1 \mathbf{b}$
and $\kappa_2 \mathbf{a} + \mathbf{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
In this basis, the model is then
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  proportional to  linear combinations of the original parameters.

Our model includes a prior that the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
If the external parameters of our model were indeed described by the \citetalias{1999PASP..111...63F}  dust model, then the prior corresponds
to the non-correlation of   $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ in the supernova sample.
A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
All color changes would then be confined to the $a(X)+\kappa_1 b(X)$ direction. This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$ .   We use this interpretation to assign  $R^F_{eff} = \kappa_1^{-1}$ as
the effective total-to-selective extinction of our sample.
\color{purple}
The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$.
Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\pmb{\gamma}^0$ and  $\mathbf{a}+\mathbf{b}/2.44$.
From the Monte Carlo chains, we find a 68\% credible interval for  $R^F_{eff}$ of 2.26--2.63.

Different supernovae are expected to encounter dust with different $R^F$.
Let us introduce a new per-supernova vector $\delta R$ such that $R^F = R^F_{eff}(1+  \delta R)$.
Variations in the value of $R^F$ (and hence $\delta R$) lead 
the prior to impose
\begin{equation}
\kappa_2 = R^F_{eff} \left(1- \frac{\mbox{Var}(\delta R\, E^F(B-V))}{\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))}\right).
\end{equation}
From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R\, E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))$.  This result indicates that there is a small but significant covariance between  extinction contributions due to
deviations from an effective $R^F$ and
the color-excess parameter $E^F(B-V)$.

%
%Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
%can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
%The zero-correlation condition, which determines the direction of $\pmb{\gamma}^1$,  is for the coordinate values along $\pmb{\gamma}^0$ to be uncorrelated with the coordinate values along $\pmb{\gamma}^1$.
%Our analysis yields an angle of 154\arcdeg\ between  $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
%The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
%Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\pmb{\gamma}^0$.
%
%
%While a similar interpretation could be made of $\kappa_2 a(X) + b(X)$, note that to first order the extinction for $\Delta R$
%perturbations from a fixed $R^F_0$ is
%\begin{equation}
%A_X = A_V \left(a(X) + \left(\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0} \right) b(X) \right).
%\end{equation}
%Then $\kappa^{-1}_2$ can this be associated with $\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0}$.
%

%To gain an intuitive understanding of how the $\kappa$ values are determined, consider the hypothetical case where
%all supernovae experience dust with the same $R^F$.   There is only one free parameter $A^F_V$ and magnitudes are
%constrained to move along the vector $a(X)+b(X)/R^F$.  In the fit of the linear model, the zero-covariance condition is satisfied when
%$-\kappa_1 A^F_V + E^F(B-V)=0$,  i.e.\ when $\kappa_1=1/R^F$.  
%Supernova magnitudes do not vary along the $\kappa_2 a(X) + b(X)$ direction.  Consequently
%$\pmb{\gamma}^0$ is aligned with  $a(X)+b(X)/R^F$, and $\pmb{\gamma}^1$ is unconstrained.

As a check of our analysis implementation, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample
(making an approximative correspondence between our observed top-hat filter colors and the 
model parameter $E^F(B-V)$) , and $R^F$ values drawn from a log-normal
distribution with a mean of $\ln{2.5}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations which yield a median
$R^F_{eff}$ of 2.53, which is close to
 the input $R^F=2.5$.

@@

Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
the former's distribution can be compared to the expectation for the latter.
Figure~\ref{k0_med:fig} shows the histogram of
median values of $\gamma^0_V k_0$ 
\color{purple}
relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
(Subtracting the value of the one supernova suppresses correlated errors in $k_0$ common to all supernovae.)
\color{black}
The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.  This distribution is given by the data, in that it is independent of any knowledge or prior
for the distribution of dust extinction the SN population is expected to suffer.

Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$
relative to that of an arbitrary supernova  $\gamma^1_V k_1|_0$, which can be attributed to 
extinction corrections due to deviations away from the canonical $R^F_{eff}$ value.   The distribution has a long
negative tail and is peaked at its positive edge. Recall that our model constraints force 
the distribution of $\gamma^1_V k_1$ has a mean of zero.
The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
of negative values associated with $R<1/\kappa_1$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$
%\color{purple}
%While at low  $\gamma^0_V k_0$
%\color{black}
%On the other hand, lower values of $\gamma^1_V k_1$
%occur at larger values of  $\gamma^0_V k_0$.
These findings are consistent with previous results:
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
%\citet{2011ApJ...729...55F} and the above authors
%find that supernovae with large extinction 
%preferentially exhibit low $R^F$.

@@

In the fit to our model, the observed color excess is attributed to 
%----
$E_{\gamma^0}(B-V)=  0.90 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.34 \pm   0.10$
%-----
contributions.
Among the supernovae in the SNfactory  set used to determine $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$, the
objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
%---
$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have $-0.01 \pm 0.01$  and
$  0.06 \pm 0.03$ 
%---
(see Figure~\ref{ebv:fig}).
The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
span of supernovae used to train the coefficients of the model, which is not unexpected if
attributable to dust.

\color{purple}
The model parameters can be transformed into  the 
\citetalias{1999PASP..111...63F} parameters using the transpose of the matrix in Eqn.~\ref{trans_I:eqn},
assuming that  SN~2011fe has zero extinction.  The colors predicted by this \citetalias{1999PASP..111...63F}--component
of our model are  shown in Figure~\ref{sn2014j:fig}. 
Our model predictions provide a significantly better match to the data
despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
Differences in the color predictions between our model and the pure dust model are
apparent,
particularly in the $B-V$ and  $R-V$ colors.  Our model has shallower decline in color excess with increasing wavelength.
(Refer to  Eqn.~\ref{res_I:eqn} to see the deviation in magnitude of our model away from the dust model.)
The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
in Figure 3 of  \citet{2014ApJ...788L..21A}, who fit
UV through NIR data to obtain $R_V^F=1.4$ and $E^F(B-V)=1.37$.
Notwithstanding their bias respect to the data, we present the transformed dust parameters
$A^F_V=0.77$ and $E^F(B-V)=1.28$ and covariance
\begin{equation}
\begin{pmatrix}
\begin{array}{rr}
0.430 & -0.004 \\
-0.004 & 0.007
\end{array}
\end{pmatrix},
\end{equation}
which imply $R^F= 0.59^{+ 0.53}_{-0.48}$.
